Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-01-21 Report/system_model.tex
changes with satya

We adopt linear transmit beamforming technique at \acp{BS}. Specifically, the data symbols \me{d_{l,k,n}} for  user \me{k} on the \me{l^\mathrm{th}} spatial stream over the sub-channel \me{n} is multiplied with beamformer \me{\mvec{m}{l,k,n} \in \mathbb{C}^{N_T \times 1}} before being transmitted. In order to detect  multiple spatial streams at the user terminal, receive beamforming vector \me{\mvec{w}{l,k,n}} is employed for each user. Consequently, the received data symbol estimate corresponding to the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n} at user $k$ is given by
\iftoggle{single_column}{
\begin{equation}\label{eqn-1}
\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n},
\end{equation}
}{
\begin{multline}\label{eqn-1}
\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n} \\ 
+ \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n},
\end{multline}
}
where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for the user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream. In \eqref{eqn-1}, \me{L = rank(\mvec{H}{b,k,n}) = min(N_T,N_R)} is the maximum number of spatial streams\footnote{\me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted}. Assuming independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
\begin{equation}\label{eq:SINR}
\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{N_0\|\mvec{w}{l,k,n}\|^2 + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}.
\end{equation}

>>>>

We adopt linear transmit beamforming technique at \acp{BS}. Specifically, the data symbols \me{d_{l,k,n}} for  user \me{k} on the \me{l^\mathrm{th}} spatial stream over the sub-channel \me{n} is multiplied with beamformer \me{\mvec{m}{l,k,n} \in \mathbb{C}^{N_T \times 1}} before being transmitted. In order to detect  multiple spatial streams at the user terminal, receive beamforming vector \me{\mvec{w}{l,k,n}} is employed for each user. Consequently, the received data symbol estimate corresponding to the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n} at user $k$ is given by
\iftoggle{single_column}{
\begin{equation}\label{eqn-1}
\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n},
\end{equation}
}{
\begin{multline}\label{eqn-1}
\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n} \\ 
+ \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n},
\end{multline}
}
where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for the user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream. In \eqref{eqn-1}, \me{L = \text{rank}(\mvec{H}{b,k,n}) = \min(N_T,N_R)} is the maximum number of spatial streams\footnote{\me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted}. Assuming independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
\begin{equation}\label{eq:SINR}
\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{\enoise + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2},
\end{equation}
where \me{\enoise = N_0\|\mvec{w}{l,k,n}\|^2} denotes the equivalent noise variance.
